Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-13 main.Rmd
example illustration of groups periodically and quasi-periodically

\todo[inline]{Give an example}

>>>>

```{r quasi-group-periodicial, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups quasi-periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$ with $E1$ as the exception."}
knitr::include_graphics("Figs/quasi_groups_periodically.png")
```

**Example**:  Example showing periodic and quasi-periodic linear granularities are displayed in \autoref{fig:group-periodicial} and \autoref{fig:quasi-group-periodicial} respectively. Each granule is represented by a box. In these figures, the granules that overlap share elements from the underlying time domain. In both of these cases, each granule of $G$ is made up of two and three granules of $B$ alternately. So the period is $P = 5$ and number of granules of $G$ in each period is given by $R=2$. The only difference in \autoref{fig:quasi-group-periodicial} is that there is an exception after the first granule of $G$ which consists of one granule of $B$. Except for this exception $E1$, $B$ groups periodically into $G$.
